---
title: "How Gen Z and Millennials are Choosing Pulse Mobile: Plan Flexibility & Community Impact (Q1 2025)"

format: 
  typst:
    toc: false
    number-sections: false
    colorlinks: true
  html:
    toc: true

editor: visual

execute:
  echo: false
  warning: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(gt)
library(ggplot2)
library(bslib)
library(knitr)
library(RColorBrewer)

source("_data.R")

brand <- attr(bslib::bs_theme(), "brand") # will be brand.yml::read_brand_yml()
```

## Intro

Pulse Mobile's rapid growth among Gen Z and Millennials reflects our commitment to transparent pricing, flexible plans, and 
genuinely impactful community initiatives that connect with the 18-30 demographic where they live, work, and play.

## Q1 2025 Pulse Performance

```{r}
#| label: summary-table

pulse_data |>
  mutate(
    total_events = event_count,
    event_engagement = paste0(round(100 * participants_per_event / total_signups, 1), "%")
  ) |>
  select(month, popular_plan, total_signups, total_events, event_participants, satisfaction_score, event_engagement) |>
  gt() |>
  tab_header(
    title = "Pulse Mobile Sign-ups & Community Engagement",
    subtitle = "Q1-Q2 2025 Performance Metrics"
  ) |>
  fmt_number(
    columns = c(total_signups, event_participants),
    decimals = 0,
    use_seps = TRUE
  ) |>
  fmt_number(
    columns = satisfaction_score,
    decimals = 1
  ) |>
  cols_label(
    month = "Month",
    popular_plan = "Most Popular Plan",
    total_signups = "Total Sign-ups",
    total_events = "Community Events",
    event_participants = "Event Participants",
    satisfaction_score = "Satisfaction Score",
    event_engagement = "Event Engagement Rate"
  ) |>
  tab_style(
    style = cell_fill(color = "#f8f9fa"),
    locations = cells_body(rows = seq(1, nrow(pulse_data), 2))
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) |>
  tab_options(
    heading.title.font.size = 18,
    heading.subtitle.font.size = 14,
    table.font.size = 12,
    heading.align = "left",
    table.border.top.width = 3,
    table.border.top.color = "#FF5733",
    table.border.bottom.color = "#FF5733",
    column_labels.border.bottom.width = 2,
    column_labels.border.bottom.color = "#33A8FF"
  )
```

## Growth Trends

```{r}
#| label: fig-signups
#| fig-cap: "The Pulse is Strong! Gen Z (18-24) continuing to lead sign-up growth with both demographics showing positive momentum."

pulse_data |>
  pivot_longer(
    cols = c(signups_18_24, signups_25_30),
    names_to = "age_group", 
    values_to = "signups"
  ) |>
  mutate(
    age_group = case_when(
      age_group == "signups_18_24" ~ "Gen Z (18-24)",
      age_group == "signups_25_30" ~ "Millennials (25-30)"
    ),
    month = factor(month, levels = c("January", "February", "March", "April", "May", "June"))
  ) |>
  ggplot(aes(x = month, y = signups, fill = age_group)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(
    title = "Monthly Sign-ups by Age Group",
    subtitle = "Q1-Q2 2025",
    x = NULL,
    y = "Number of Sign-ups",
    fill = "Age Group"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12),
    legend.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  if (!is.null(brand)) {
    scale_fill_manual(
      values = unlist(set_names(
        brand$color$palette[c("purple", "blue")],
        c("Gen Z (18-24)", "Millennials (25-30)")
      ))
    )
  }
```

```{r}
#| label: fig-events
#| fig-cap: "Community Vibes Rising! Participation in Pulse Mobile events showing strong upward trajectory as we expand our authentic connection with customers."

g <- pulse_data |>
  ggplot(aes(
    x = factor(
      month,
      levels = c("January", "February", "March", "April", "May", "June")
    )
  )) +
  geom_line(
    aes(y = event_participants, group = 1, color = "Participants"),
    size = 1.5
  ) +
  geom_point(aes(y = event_participants, color = "Participants"), size = 3) +
  geom_bar(
    aes(y = event_count * 30, fill = "Events"),
    stat = "identity",
    alpha = 0.5
  ) +
  scale_y_continuous(
    name = "Number of Participants",
    sec.axis = sec_axis(~ . / 30, name = "Number of Events", breaks = 1:10)
  ) +
  labs(
    title = "Community Event Participation",
    subtitle = "Growth in events and engagement over time",
    x = NULL
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
if (!is.null(brand)) {
  g +
    scale_color_manual(
      values = c("Participants" = brand$color$palette$blue),
      name = NULL
    ) +
    scale_fill_manual(
      values = c("Events" = brand$color$palette$purple),
      name = NULL
    )
} else {
  g
}
```

## Pulse Check (Analysis)

The data doesn't lie, and neither do we! Our Q1-Q2 performance shows Pulse Mobile isn't just growing—we're creating genuine 
connections. Gen Z continues to lead our sign-up growth (averaging nearly 60% of new customers), while our community events 
are absolutely crushing it with participation up 210% from January to June.

As our community expands, so does customer satisfaction—reaching an all-time high of 4.7 in June. This isn't just about 
selling phone plans; it's about building a movement where transparent pricing meets authentic community impact. The shift in 
popular plans from "Flex" to "Community" shows our audience isn't just looking for flexibility; they want to feel part of 
something bigger.

Social mentions have more than doubled over six months, proving that when you create genuine connections, people actually 
want to talk about you! With event engagement consistently above 25% of our customer base, Pulse Mobile isn't just a service 
provider—we're becoming an essential part of our customers' social landscape.

Let's keep this momentum going and continue to disrupt the industry with plans that make sense and community initiatives that
make a difference. The pulse is strong, and it's beating to our own rhythm!