---
title: "How Gen Z and Millennials are Choosing Pulse Mobile"
subtitle: "Plan Flexibility & Community Impact (Q1 2025)"
format:
  revealjs:
    theme: default
    footer: "Pulse Mobile | Q1-Q2 2025"
    transition: slide
    background-transition: fade
    highlight-style: github
execute:
  echo: false
  warning: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(gt)
library(ggplot2)

source("_data.R")

brand <- attr(bslib::bs_theme(), "brand") # will be brand.yml::read_brand_yml()
```

## Our Mission

Transparent pricing, flexible plans, and community-focused initiatives that resonate with the 18-30 demographic.

## Q1-Q2 Snapshot {.smaller}

:::: {.columns}

::: {.column width="50%"}
### The Numbers
- **1,970+** total sign-ups in Q1-Q2
- **60%** from Gen Z (18-24)
- **40%** from Millennials (25-30)
- **33** total community events
- **1,005** event participants
:::

::: {.column width="50%"}
### Key Insights
- Satisfaction score increased from **4.2** to **4.7**
- Social mentions up **149%** 
- Most popular plan shifted from "Flex" to "Community"
- Event participation per customer **growing steadily**
:::

::::

## The Pulse is Strong!

```{r}
#| label: fig-signups
#| fig-width: 10
#| fig-height: 6
#| fig-align: center

pulse_data |>
  pivot_longer(
    cols = c(signups_18_24, signups_25_30),
    names_to = "age_group",
    values_to = "signups"
  ) |>
  mutate(
    age_group = case_when(
      age_group == "signups_18_24" ~ "Gen Z (18-24)",
      age_group == "signups_25_30" ~ "Millennials (25-30)"
    ),
    month = factor(
      month,
      levels = c("January", "February", "March", "April", "May", "June")
    )
  ) |>
  ggplot(aes(x = month, y = signups, fill = age_group)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(
    aes(label = signups, group = age_group),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  labs(
    title = "Monthly Sign-ups by Age Group",
    subtitle = "Q1-Q2 2025",
    x = NULL,
    y = "Number of Sign-ups",
    fill = "Age Group"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 24),
    plot.subtitle = element_text(size = 18),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14),
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 16),
    legend.text = element_text(size = 14),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 14)
  ) +
  if (!is.null(brand)) {
    scale_fill_manual(
      values = unlist(set_names(
        brand$color$palette[c("purple", "blue")],
        c("Gen Z (18-24)", "Millennials (25-30)")
      ))
    )
  }
```

## By The Numbers {.smaller}

```{r}
pulse_data |>
  mutate(
    total_events = event_count,
    event_engagement = paste0(round(100 * participants_per_event / total_signups, 1), "%")
  ) |>
  select(month, popular_plan, total_signups, total_events, event_participants, satisfaction_score) |>
  gt() |>
  tab_header(
    title = "Pulse Mobile Performance Metrics",
    subtitle = "Q1-Q2 2025"
  ) |>
  fmt_number(
    columns = c(total_signups, event_participants),
    decimals = 0,
    use_seps = TRUE
  ) |>
  fmt_number(
    columns = satisfaction_score,
    decimals = 1
  ) |>
  cols_label(
    month = "Month",
    popular_plan = "Top Plan",
    total_signups = "Sign-ups",
    total_events = "Events",
    event_participants = "Participants",
    satisfaction_score = "Satisfaction"
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  )
```

## What We're Seeing {.incremental}

- **Gen Z dominance**: Consistently representing ~60% of our new sign-ups
- **Shifting preferences**: Plans with community impact gaining traction
- **Engagement growth**: Event participation up 210% since January
- **Digital buzz**: Social mentions more than doubled in six months
- **Customer love**: Satisfaction scores reached all-time high of 4.7

## Why This Matters

We're not just selling phone plans. We're building a movement.

## Next Steps {.smaller}

:::: {.columns}

::: {.column width="50%"}
### Double Down On
- Community-focused plans and events
- Transparent messaging around flexible options
- Local initiatives that drive engagement
- Digital storytelling featuring real customers
:::

::: {.column width="50%"}
### Areas to Explore
- Targeted offerings for Gen Z's specific needs
- Expanding community events to new markets
- Social cause partnerships with authentic alignment
- Referral programs to amplify word-of-mouth
:::

::::

## Thank You!

Questions?